Verifying Demonstrations

### 2018-11-21 paper/privacy-properties.tex
Writes up verifiability and privacy properties (definitions)

Finally, any temporary identifiers, such as pseudonyms, should only be reused 
when strictly necessary for the fulfillment of verifiability properties (in 
\cref{verifiability-properties}) to prevent inference on long-term identities 
by repeated samples and side information.

We can thus summarize the desired privacy properties as follows:
\begin{requirements}[P]
\item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: every 
  participant's (protester and witness) real (long-term) identity (\(P\)) must 
  be unlinkable to their participation proofs \(\prf_{\pid, \prtst}\)
\item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters' participation proofs \(\prf_{\pid, \prtst}\) must be unlinkable between protests (\(\cid, \cid' \))
\item\label{WitnessUnlink}\emph{Witness Unlinkability}:  witnesses' participation proof shares \(\psh = (\cid, t, l, \pid,\wid)\) must be unlinkable between protesters. (\(\pid, \pid' \))
\end{requirements}

In light of these definitions, we note that \cref{CountOnce} can be rephrased 
in terms of pseudonyms as follows:
\begin{enumerate}
  \item[V1.3.] \emph{Counted only once}:
    A protester can create \emph{only one} pseudonym per protest, this 
    pseudonym is unique except with negligible probability.
\end{enumerate}

%Seb: ok for me, I have put it in comment
%\sonja{removed for now: As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
%This is, in fact, is a slight increase in privacy over ordinary protests.}

>>>>

For privacy, any temporary identifiers, such as pseudonyms, should only be 
reused when strictly necessary (by the principle of data minimization) for the 
fulfillment of verifiability properties (in \cref{verifiability-properties}) to 
prevent inference on long-term identities by repeated samples and side 
information.
We can thus summarize the desired privacy properties as follows:
\begin{requirements}[P]
\item\label{PseudonymUnlink} \emph{Pseudonym unlinkability}: given a protest 
  (identifier \cid), protesters Alice and Bob, and a pseudonym \(\pid_b\), the 
  adversary cannot tell if \(\pid_b = \pid_{\text{Alice}}\) or \(\pid_b = 
    \pid_{\text{Bob}}\), except with negligible probability.
\item\label{ProtestUnlink} \emph{Protest unlinkability}: protesters' pseudonyms 
  (\(\pid_\cid, \pid_{\cid'}\)) must be unlinkable between protests (\(\cid, 
    \cid'\)) from the adversary's perspective.
\item\label{WitnessUnlink}\emph{Witness unlinkability}:  witnesses' pseudonyms 
  (\(\wid_\pid, \wid_{\pid'}\)) must be unlinkable between protesters (\(\pid, 
    \pid'\)) from the adversary's perspective.
\end{requirements}

What these properties say is that pseudonyms must look random 
(\cref{PseudonymUnlink}) and that each pseudonym must be used at most once 
(\cref{ProtestUnlink,WitnessUnlink}).

### 2018-11-21 paper/verifiability-properties.tex
Moves intuition for properties to system-model
Writes up verifiability and privacy properties (definitions)

To adapt these properties to the context of protests, we define three 
verifiability requirements, among which eligibility can be further broken up 
into four subproperties:
\begin{requirements}[V]
  \item\label{EligibilityVerif} \emph{Eligibility}: anyone can verify that each participation proof provides temporal and spatial eligibility and that only one participation proof is counted per individual.
    \begin{requirements}
    \item\label{TemporallyRelated} \emph{Temporal eligibility}: demonstrate that the proof was created after the start of the protest and before the end of the protest.
    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: demonstrate that the proof is spatially related to the physical location or journey of the protest.
    \item\label{CountOnce} \emph{Counted only once}: prove that no individual 
      can be counted more than once for a particular protest.
      \seb{this property seems to be related to the eligibility property in the 
        sense that if a participant tries to submit a second proof this 
        directly conflicts with the eligibility}
      \daniel{Yes, that's why it's a sub-property of eligibility, we're trying 
        to make eligibility more concrete.}
    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated with particular designated protest.
    \end{requirements}

>>>>

We now try to make the properties from \cref{desired-properties} more 
specific.
We define three verifiability requirements, among which eligibility can be 
further broken up into four subproperties:
\begin{requirements}[V]
  \item\label{EligibilityVerif} \emph{Eligibility}: anyone can verify that each participation proof provides temporal and spatial eligibility and that only one participation proof is counted per individual.
    \begin{requirements}

    \item\label{TemporallyRelated} \emph{Temporal eligibility}: demonstrate that the proof was created after the start of the protest and before the end of the protest.

    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: demonstrate that the proof is spatially related to the physical location or journey of the protest.

    \item\label{CountOnce} \emph{Counted only once}:
      A protester can create \emph{one and only one} pseudonym per protest 
      (\(\pid\) in \cref{DefProofShares}), this pseudonym is unique except with 
      negligible probability.
      Analogously, a witness can create \emph{one and only one} pseudonym per 
      protester (\(\wid\) in \cref{DefProofShares}), this pseudonym is unique 
      except with negligible probability.

    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated with particular designated protest.

    \end{requirements}
